Sound Automated Synthesis of Digital Controllers

### 2016-10-08 paper/paper.tex
nudged the title
Review of quantization error chapter

\title{
Sound and Automated Synthesis of Digital Controllers for Physical Plants 
%Counterexample-guided Synthesis of Closed-loop Digital Control Systems
}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Modelling Errors}

In this section, we show how to embed discretisation errors on the plant model, as follows: 
%$\hat{G}(z)$ is split into two terms:
%
\begin{equation}
\label{eq:uncertainplant}
%\hat{G}(z)=G(z)+\Delta{G(z)},
\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
\end{equation}
where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$, 
$\Delta{G_{Q}(z)}$ represents the quantisation uncertainty model, 
and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.

@@

\subsection{An Uncertainty Model for the Quantization Error} 
\label{sec:uncertainty-model-quantization-error}

@@

Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem} \red{[requires updating]},
where $C(z)$ is the digital controller model, whose control output signal is
quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
converter (DAC). The quantization occurs because the DAC resolution may be different from the fixed point representation of the controller.  
$G(s)$ is the continuous-time model of the plant, from
which output samples are taken and quantized ($Q1$) by means of an
analog-to-digital converter (ADC) synchronized with the DAC.  Each quantizer
($Q1$ and $Q2$) will present some contribution for the total quantization
noise.
%    
\begin{figure}[ht]
\centering

@@

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.5cm, column sep=.5cm] {
    \node[draw=none] (r) {r};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde u(z)$};

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu2$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(s)}};
   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$u(s)$};
   \& \coordinate (aux1);
   \& \node[draw=none] (y) {y};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

  \path[->] (v1) edge (q1.north);
  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (y);
  \path  
   (circle.east) edge (switch1)
   (switch2) edge (q1.west)
   (q1.east) edge (cz.west)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (gs.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Sampled System. \label{fig:sampledsystem} \red{[Please update this figure: reference enters downstream of control block. Clarify signals over lines in plot.]}}
\end{figure}

@@

First, some assumptions have to be established to obtain a model for $\Delta{G_{Q}(z)}$. 
\blue{[Here we need to be careful: we first argue that quantisation (spelled with an s, so that ER II is happy) effects can be represented as an additive noise (great), which however is a stochastic signal. But we handle the noise deterministically. How so? Where is the catch? ]}
%
\begin{myassumption}
\label{whitenoise}
%
The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are white noises.
%
\end{myassumption}

\begin{myassumption}
The quantization noises $\nu_{1}$ and $\nu_{2}$ are uncorrelated with each other.
\end{myassumption}

@@

\begin{myassumption}
%
The DAC interpolator is an ideal ZOH; it takes the discrete value of control
signal $\tilde u(k)$ at instant $k$ and produces a rectangular pulse of height
$u(k)$ and width equal to the sample time $T$. \red{[Right: so under this assumption, we really only focus on the quantisation effects introduced by the ADC, correct? Let us not mix up the role and the influence of the two blocks.]}
%
\end{myassumption}

Given those assumptions, the present approach is further based on the following lemmas. 
\red{[So we have introduced two quantisation errors, properly indexed. Next we discuss a non-indexed entity - pls clarify or comment.]}
%
\begin{mylemma}
%
\cite{widrow1956} The second moment (variance) of the probability probability density function of quantization
noise is given by %\textcolor{red}{expand the acronym PDF}
%
\begin{equation}
\label{eq:variancelemma}
\sigma_{Q}^{2}=\frac{q^{2}}{12},
\end{equation}
\end{mylemma}
where $q$ is the step size of quantizer. \blue{[can you add a comment on this assumption? Why the factor 12?]}

\begin{myprop}
Considering the quantisation noise $\nu(k)$ as an output error in the
discrete plant model, 
%{\it i.e.}, it does not affect the plant dynamics, but its output samples, 
$\Delta{G_{Q}(z)}$ can be obtained from
%
\begin{equation}
\label{eq:quantization_tf}
\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
\end{equation}
where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
which can be calculated through the power spectral density of
$\nu(k)$~\cite{poularikas2000transforms}.  
Thus, the $\Delta{G_{Q}(z)}$ can expressed as
%
\begin{equation}
\label{eq:deltag_var}
\Delta{G_{Q}(z)}=\frac{\sigma_{Q}^{2}}{U(z)},
\end{equation}
where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
the signal from the digital controller), which is provided to the plant by
means of ZOH.
\end{myprop}

%
\begin{proof}
%
Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
be represented by the following pulse transfer function (without
quantization noise effect):
%
\begin{equation}
\label{eq:tfwithout}
G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
\end{equation}
%
\noindent where $Y(z)$ is the z-transform of the plant output signal without
noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
function numerator and denominator, respectively.

Considering the quantization noise $\nu(k)$ as an output error in the
discrete plant model, an additive noise in the plant output $y(k)$ resulting
in the noisy output $\hat{y}(k)$ can be represented as
%
\begin{equation}
\hat{y}(k)=y(k)+\nu(k).
\end{equation}

Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the
following difference equation:
%
\begin{equation}
\begin{split}
y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
\end{split}
\end{equation}

\noindent and consequently $\hat{y}(k)$ can be represented by the following
difference equation:
%
\begin{equation}
\label{eq:differencewithnoise}
\begin{split}
\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M)+\nu(k).
\end{split}
\end{equation}

The z-transform of Eq.~\eqref{eq:differencewithnoise} is
%
\begin{equation}
\begin{split}
\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N}z^{-N})Y(z)\\
+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M})U(z)+\nu(z),
\end{split}
\end{equation}
dividing both sides by $U(z)$, it is equivalent to:
\begin{equation}
\frac{\hat{Y}(z)}{U(z)}=\hat{G}(z)=[1-A(z)]G(z)+U(z)B(z)+\frac{\nu(z)}{U(z)}.
\end{equation}

Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout},
the intended expression can be obtained as
%
\begin{equation}
\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)} 
\end{equation}
\end{proof}

Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
effect on the plant transfer function demands an estimation of the variance
of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
methodology presented by~\cite{widrow2008quantization}
is used.  The authors provide an algorithm for computing the mean square of
the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
contribution can be represented by a white noise with zero mean
(Assumption~\ref{whitenoise}), the mean square can be considered as the
variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
%
\begin{equation}
\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
\end{equation}
%
\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]} 
for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.

The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
sums of the impulse response are needed, can be obtained through the
analysis of the system in Figure~\ref{fig:sampledsystem}.  Considering that
the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
following equation can be written for the system in
Figure~\ref{fig:sampledsystem}
%
\begin{equation}
\resizebox{0.48\textwidth}{!}{
$\hat{Y}(z)=\nu_{1}(z)C(z)G(z)+\nu_{2}(z)G(z)+R(z)C(z)G(z)-\hat{Y}(z)C(z)G(z),$
}
\end{equation}

\noindent which can be rewritten as
%
\begin{equation}
\label{eq:outputfunctions}
\resizebox{0.48\textwidth}{!}{
$\hat{Y}(z)=\frac{C(z)G(z)}{1+C(z)G(z)}R(z)+\frac{C(z)G(z)}{1+C(z)G(z)}\nu_{1}(z) \\
+\frac{G(z)}{1+C(z)G(z)}\nu_{2}(z).$
}
\end{equation}

Thus, $H_{Q1}(z)$ and $H_{Q2}(z)$ can be extracted from Eq.~\eqref{eq:outputfunctions}:
\begin{equation}
H_{Q1}(z)=\frac{C(z)G(z)}{1+C(z)G(z)},
\end{equation}
and
\begin{equation}
H_{Q2}(z)=\frac{G(z)}{1+C(z)G(z)}.
\end{equation}

These equations are sufficient for computing $\sigma_{Q}^{2}$.  However,
there is still a gap for a complete model for $\Delta{G_{Q}(z)}$ in
Eq.~\eqref{eq:deltag_var}, {\it i.e.}, the z-transform of control action
$U(z)$.  This indicates that the quantization noise effect on a discrete
plant model mainly depends on three main factors:
%
\begin{itemize}
%
\item \textbf{Sample time:} the sample time effect is reflected over pulse transfer function that covers the effects of DAC ant its interpolator (ZOH) \red{[clarify/revise based on the comments made above.]};
%
\item \textbf{ADC and DAC step:} \red{[again, do we need both?]} these are the main component of quantization noise power, but an $8$-bits converter already reduces the effect of quantization noises in the output for negligible values.
%
\item \textbf{Signal-to-noise ratio (SNR): } the dependence on the value of $U(z)$ \red{[notice that now we have reduced the problem to depend on the effect of the reference signal transform R(z) - pls revise.]} shows the importance of the SNR for handling quantization noise; for a high SNR of the digital controller, the quantization effect is negligible. This happens during the transient of the system, when high control actions are employed. However, it can be relevant during the steady state. A digital controller with integral action might be sufficient for eliminating such influence at steady state.
%
\end{itemize}

An alternative expression for $\Delta{G_{Q}(z)}$ can be obtained from
Eq.~\eqref{eq:deltag_var}, transforming it into a function of the reference
$R(z)$.  Once $U(z)$ is the control signal obtained via digital controller
$C(z)$ and error signal, {\it i.e.},
%
\begin{equation}
U(z)=C(z)\cdot[R(z)-Y(z)],
\end{equation}

\noindent where $Y(z)$ is the first term of Eq.~\eqref{eq:outputfunctions}, thus:
\begin{equation}
\label{eq:controlsignal}
\resizebox{0.48\textwidth}{!}{
$U(z)=C(z)\cdot \left[R(z)-\frac{C(z)G(z)}{1+C(z)G(z)}R(z)\right]=\frac{C(z)}{1+C(z)G(z)}R(z).$
}
\end{equation}

Substituting Eq.~\eqref{eq:controlsignal} in Eq.~\eqref{eq:deltag_var}, a
model for $\Delta{G_{Q}(z)}$ depending on $R(z)$ can be obtained:
%
\begin{equation}
\Delta{G_{Q}(z)}=\sigma^{2}_{Q}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{1}{R(z)},
\end{equation}

\noindent where $R(z)$ can be considered as a step signal (for stabilization
purpose) with height equal to $r$, which can be rewritten as
%
\begin{equation}
\Delta{G_{Q}(z)}=\frac{\sigma^{2}_{Q}}{r}\cdot \frac{1+C(z)G(z)}{C(z)} \cdot \frac{z-1}{z}.
\end{equation}

>>>>

\title{
Sound Automated Synthesis of Digital Controllers
%Counterexample-guided Synthesis of Closed-loop Digital Control Systems
}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Modelling Errors}

%In this section, we show how to embed discretisation errors on the plant model, as follows: 
%%$\hat{G}(z)$ is split into two terms:
%%
%\begin{equation}
%\label{eq:uncertainplant}
%%\hat{G}(z)=G(z)+\Delta{G(z)},
%\tilde G(z) = \hat G(z) + \Delta G_P(z) = G(z,T) + \Delta G_Q(z) + \Delta G_P(z),   
%\end{equation}
%where $G(z,T)$ is the time discretisation of the nominal physical plant $G(s)$, 
%$\Delta{G_{Q}(z)}$ represents the quantisation uncertainty model, 
%and $\Delta{G_{P}(z)}$ describes the parametric uncertainty model.

@@

\section{An Uncertainty Model for the Quantization Error} 
\label{sec:uncertainty-model-quantization-error}

@@

Consider the closed-loop sampled system in Figure~\ref{fig:sampledsystem},
where $C(z)$ is the digital controller model, whose control output signal is
quantized ($Q2$) and interpolated via a ZOH using digital-to-analog
converter (DAC). The quantization occurs because the DAC resolution may be different from the fixed point representation of the controller.  
$G(s)$ is the continuous-time model of the plant, from
which output samples are taken and quantized ($Q1$) by means of an
analog-to-digital converter (ADC) synchronized with the DAC.  Each quantizer
($Q1$ and $Q2$) will present some contribution for the total quantization
noise.
%    
\begin{figure}[ht]
\centering

@@

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center}, row sep=.6cm, column sep=.3cm] {
    \node[draw=none] (r) {r(z)};
%   \& \coordinate (aux0);
   \& \node[circle,add={-}{+}{}{}] (circle) {};
   \node[draw=none] (ez) at ([xshift=1cm,yshift=.15cm]circle)  {$\tilde e(z)$};
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Controller}] (cz) {{\sc C(z)}};
   \node[draw=none] (ud) at ([xshift=1cm,yshift=.15cm]cz)  {$\tilde u(z)$};

   \& complexnode/.pic={ 
      \node[rectangle,draw,
	minimum width=3cm,
	minimum height=1.6cm,
	label=\textbf{DAC},] (dac) {};
     \node[circle,add={}{+}{+}{},fill=yellow!20] (q2) at ([xshift=-.65cm]dac.center) {};
     \node[draw=none] (q2t)  at ([xshift=-.65cm,yshift=-.65cm]dac.center) {{\sc Q2}};
     \node[draw=none] (v2)  at ([xshift=-.65cm,yshift=1.5cm]dac.center) {$\nu2$};
     \node[fill=yellow!20] (zoh) at ([xshift=.65cm]dac.center) {{\sc ZOH}};}
   \& \node[rectangle,draw,
	minimum width=1cm,
	minimum height=1cm,
        label=\textbf{Plant}] (gs) {{\sc G(s)}};
   \node[draw=none] (ud) at ([xshift=-1cm,yshift=.15cm]gs)  {$u(s)$};
   \node[draw=none] (y) at ([xshift=1cm,yshift=.15cm]gs)  {$y(s)$};
   \& complexnode/.pic={ 
     \node[rectangle,draw,
	minimum width=4cm,
	minimum height=1.6cm,
	label=\textbf{ADC},] (adc) {};
   \draw[] ([xshift=-1cm]adc.center) -- ++(0.5,0.2cm);
   \coordinate (switch1) at ([xshift=-1cm]adc.center);
   \coordinate (switch2) at ([xshift=-0.4cm]adc.center);
   \node[circle,add={}{+}{+}{},fill=yellow!20] (q1) at ([xshift=1cm]adc.center) {};} 
     \node[draw=none] (q2t)  at ([xshift=1cm,yshift=-.65cm]adc.center) {{\sc Q1}};
   \node[draw=none] (v1)  at ([xshift=1cm,yshift=1.5cm]adc.center) {$\nu1$};
   \& \coordinate (aux1);
   \& \node[draw=none] (yz) {$\tilde y(z)$};\\
   \& \coordinate (aux3); 
   \&
   \&
   \& 
   \& 
   \& \coordinate (aux2);\\
  };

  \path[->] (v1) edge (q1.north);
  \path[->] (v2) edge (q2.north);
  \path[->] (r) edge (circle.west);
  \path[->] (aux1) edge (yz);
  \path  
   (circle.east) edge (cz)
   (cz.east) edge (q2.west)
   (q2.east) edge (zoh.west)
   (zoh.east) edge (gs.west)
   (switch2) edge (q1.west)
   (q1.east) edge (aux1.west)
   (gs.east) edge (switch1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Sampled System. \label{fig:sampledsystem}}
\end{figure}

@@

First, some assumptions have to be established to obtain a model for the quantization effects (seen as noise) on the closed loop system. 
%
\begin{myassumption}
\label{whitenoise}
%
The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are energy bounded uncorrelated white noises.

In \cite{widrow1956}, Widrow models the quantization noise as a gaussian model in which
the second moment (variance) of the probability density function (pdf) of the quantization
noise is given by
%
\begin{equation}
\label{eq:variancelemma}
\sigma_{Q}^{2}=\frac{q^{2}}{12},
\end{equation}
where $q$ is the step size of quantizer, thus supporting this assumption.
\end{myassumption}

@@

\begin{myassumption}
%
The DAC interpolator is an ideal ZOH; it takes the discrete value of control
signal $\tilde u(k)$ at instant $k$ and produces a rectangular pulse of height
$u(k)$ and width equal to the sample time $T$.
%
\end{myassumption}

%\begin{myprop}
%Considering the quantisation noise $\nu(k)$ as an output error in the
%discrete plant model, 
%%{\it i.e.}, it does not affect the plant dynamics, but its output samples, 
%$\Delta{G_{Q}(z)}$ can be obtained from
%%
%\begin{equation}
%\label{eq:quantization_tf}
%\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)},
%\end{equation}
%where $\nu(z)$ is the z-transform of the random process $\nu(k)$,
%which can be calculated through the power spectral density of
%$\nu(k)$~\cite{poularikas2000transforms}.  
%Thus, the $\Delta{G_{Q}(z)}$ can expressed as
%%
%\begin{equation}
%\label{eq:deltag_var}
%\Delta{G_{Q}(z)}=\frac{\sigma_{Q}^{2}}{U(z)},
%\end{equation}
%where $\sigma_{Q}^{2}$ is the variance of the quantization noise and
%$U(z)$ is the z-transform of control signal ({\it i.e.}, the z-transform of
%the signal from the digital controller), which is provided to the plant by
%means of ZOH.
%\end{myprop}
%
%%
%\begin{proof}
%%
%Suppose that the plant discrete model in Figure~\ref{fig:sampledsystem} can
%be represented by the following pulse transfer function (without
%quantization noise effect):
%%
%\begin{equation}
%\label{eq:tfwithout}
%G(z)=\frac{Y(z)}{U(z)}=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M}}{1+a_{1}z^{-1}+a_{2}z^{-2}+\cdots+a_{N}z^{-N}},
%\end{equation}
%%
%\noindent where $Y(z)$ is the z-transform of the plant output signal without
%noise $y(k)$, $U(z)$ is the z-transform of the control signal, which is
%provided to the plant, $A(z)$ and $B(z)$ are the plant pulse transfer
%function numerator and denominator, respectively.
%
%Considering the quantization noise $\nu(k)$ as an output error in the
%discrete plant model, an additive noise in the plant output $y(k)$ resulting
%in the noisy output $\hat{y}(k)$ can be represented as
%%
%\begin{equation}
%\hat{y}(k)=y(k)+\nu(k).
%\end{equation}
%
%Note that the model in Eq.~\eqref{eq:tfwithout} is equivalent to the
%following difference equation:
%%
%\begin{equation}
%\begin{split}
%y(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M),
%\end{split}
%\end{equation}
%
%\noindent and consequently $\hat{y}(k)$ can be represented by the following
%difference equation:
%%
%\begin{equation}
%\label{eq:differencewithnoise}
%\begin{split}
%\hat{y}(k)=-a_{1}y(k-1)-a_{2}y(k-2)-\cdots - a_{N}y(k-N)\\
%+b_{0}u(k)+b_{1}u(k-1)+b_{2}u(k-2)+\cdots+b_{M}u(k-M)+\nu(k).
%\end{split}
%\end{equation}
%
%The z-transform of Eq.~\eqref{eq:differencewithnoise} is
%%
%\begin{equation}
%\begin{split}
%\hat{Y}(z)=(-a_{1}z^{-1}-a_{2}z^{-2}-\cdots-a_{N}z^{-N})Y(z)\\
%+(b_{0}+b_{1}z^{-1}+b_{2}z^{-2}+\cdots+b_{M}z^{-M})U(z)+\nu(z),
%\end{split}
%\end{equation}
%dividing both sides by $U(z)$, it is equivalent to:
%\begin{equation}
%\frac{\hat{Y}(z)}{U(z)}=\hat{G}(z)=[1-A(z)]G(z)+U(z)B(z)+\frac{\nu(z)}{U(z)}.
%\end{equation}
%
%Considering $\hat{G}(z)=G(z)+\Delta{G_{Q}(z)}$ and Eq.~\eqref{eq:tfwithout},
%the intended expression can be obtained as
%%
%\begin{equation}
%\Delta{G_{Q}(z)}=\frac{\nu(z)}{U(z)} 
%\end{equation}
%\end{proof}

%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
%effect on the plant transfer function demands an estimation of the variance
%of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
%methodology presented by~\cite{widrow2008quantization}
%is used.  The authors provide an algorithm for computing the mean square of
%the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
%contribution can be represented by a white noise with zero mean
%(Assumption~\ref{whitenoise}), the mean square can be considered as the
%variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
%%
%\begin{equation}
%\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
%\end{equation}
%%
%\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]} 
%for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
%{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
%of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
%
%The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
%sums of the impulse response are needed, can be obtained through the
%analysis of the system in Figure~\ref{fig:sampledsystem}. 
Considering that
the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
following equation can be written for the system in
Figure~\ref{fig:sampledsystem}
%
\begin{equation}
\resizebox{0.48\textwidth}{!}{
$\hat{Y}(z)=\nu_{1}(z)C(z)G(z)+\nu_{2}(z)G(z)+R(z)C(z)G(z)-\hat{Y}(z)C(z)G(z),$
}
\end{equation}

\noindent which can be rewritten as
%
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}(z)\left(R(z)+\nu_{1}(z)\right)+H_{2}(z)\nu_{2}(z)
\end{equation}
$$H_{1}(z)=\frac{C(z)G(z)}{1+C(z)G(z)}$$
$$H_{2}(z)=\frac{G(z)}{1+C(z)G(z)}$$
